---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bcadata

<!-- badges: start -->
[![R-CMD-check](https://github.com/vfci/vfci/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/vfci/vfci/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

This package, `bcadata` replicates and updates the data used by Angeletos, Collard, and Dellas in their paper "[Business Cycle Anatomy](https://www.aeaweb.org/articles?id=10.1257/aer.20181174)".

> Angeletos, George-Marios, Fabrice Collard, and Harris Dellas. 2020. "Business-Cycle Anatomy." American Economic Review, 110 (10): 3030-70.

The package pulls most of the data from [FRED](https://fred.stlouisfed.org) and TFP data from the [San Francisco Fed](https://www.frbsf.org/economic-research/indicators-data/total-factor-productivity-tfp/).

The data series constructed are:

* output, Real GDP per capita
* investment, Real investment per capita 
* consumption, Real consumption per capita 
* hours_worked, Hours Worked 
* unemployment, Unemployment Rate (as percent) 
* labor_share, Labor share of output 
* interest, Fed Funds interest rate (quarterly rate, not annual) 
* inflation, Inflation rate, from GDP price deflator 
* productivity, Productivity (NFB) 
* TFP, Total Factor Productivity cummulative 

## Installation

You can install the development version of bcadata from [GitHub](https://github.com/) with:
``` r
# install.packages("devtools")
devtools::install_github("VFCI/bcadata")
```

## FRED API Key

This package requires a FRED API key to pull data from the St. Louis Fed.

You can get an API key [here](https://fred.stlouisfed.org/docs/api/api_key.html).

```{r, include = F}
  ## Please get your own key from FRED
  my_api_key <- "7fdf94c38c6355269067736a82bf7874"
```

## Usage
```{r}
  library(bcadata)
```

There are two functions exported from the package:

```{r update, include = T, echo = T}
## Construct the updated data series
df <- pull_bcadata(fred_api_key = my_api_key)

## Chart comparing the updated series to the original data
compare_bcadata(df)
```

The package includes the original dataset from the [author's replication files](https://www.openicpsr.org/openicpsr/project/118082/version/V1/view).
``` r 
original_bcadata
```

## Vintage data

There is also an option to use vintage data for the data pulled from FRED.
This makes use of [ALFRED](https://alfred.stlouisfed.org), the archival version of FRED.

To pull data using a specific vintage date:

``` r
df <- pull_bcadata(fred_api_key = "XXXXXXXXXXXX", vintage_date = "2020-01-01")
```

## Replication of Original BCA data

With specific validation dates, this package can replicate the data used in the BCA paper.

Data for TFP is pulled from [John G. Fernald's website](https://www.johnfernald.net/TFP) where he stores archived versions of the TFP data hosted at the San Francisco Fed.
To replicate the original paper, the package pulls the file `data_quarterly_2018.05.03.xlsx`.

For the other macro time series, all are pulled using ALFRED, using the validation date of `"2018-07-26"`, except for the series for real GDP, which is pulled using the validation date `"2018-07-28"`.

This is accomplished by setting the paramter `replicate` to `TRUE`.
Note that TFP is off by a constant value of `20.26` from the original data.
The original author's code does not make clear why or how this adjustment was made, so this package does not make it.

```{r replicate, include = T, echo = T, warning = F}

replication <- pull_bcadata("XXXXXXXXXXXX", replicate = TRUE)

compare_bcadata(replication)
```
